%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Aayush}{Gupta}{ \urlstyle{same}\href{https://aboutme.wafercode.com}{aboutme.wafercode.com}| \href{https://www.linkedin.com/in/agadmin/}{www.linkedin.com/in/agadmin}\\
\href{mailto:aayush23467@gmail.com}{aayush23467@gmail.com} | +91-828.753.11 | \href{mailto:agcdev0@gmail.com}{agcdev0@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Jamia Millia Islamia}
\descript{BS/B.Tech in ECE}
\location{2021-2025 | New Delhi, India}
Faculty of Engineering and Technology \\
% Magna Cum Laude\\
% \location{ Cum. GPA: 3.83 / 4.0 \\
% Major GPA: 3.9 / 4.0}
\sectionsep

\subsection{DPSG, Meerut Road}
\location{Grad. April 2020| Ghaziabad, India}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/aayush-ag}{\bf aayush-ag} \\
LinkedIn://  \href{https://www.linkedin.com/in/agadmin}{\bf linkedin.com/in/agadmin} \\
Kaggle:// \href{https://www.kaggle.com/agadmin}{\bf agadmin} \\
Twitter://  \href{https://twitter.com/agcdev0}{\bf @agcdev0} \\
Quora://  \href{https://www.quora.com/profile/Aayush-Gupta-198}{\bf Aayush-Gupta-198}
% YouTube://  \href{https://www.youtube.com/user/DeedyDash007}{\bf DeedyDash007} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Computer Architecture \\
DBMS \\
Microprocessor \\
Signal and Systems \\
Assembly Language \\
Control Systems \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}

\subsection{Programming}
Rust \textbullet{} C++ \textbullet{} Python \textbullet{} Javascript \\
Golang \textbullet{} MEAN Stack \textbullet{} Rails \\
\textbullet{} C \textbullet{} PHP \textbullet{} CSS

\subsection{In Learning}
Machine Learning (ML) \textbullet{} Data Science (DS)

\subsection{Tools}
Docker \textbullet{} Terraform \textbullet{} Ansible \\
PAAS (Heroku, etc.) \textbullet{} IAAS (GCP/AWS) (VM’s, VPC Architecture) \\
Git \textbullet{} Kubernetes \textbullet{} MySQL \textbullet{} MongoDB \\
Colab \textbullet{} Kaggle \textbullet{} Wordpress \textbullet{} FFMPEG \\
... and growing
\sectionsep

\section{Certifications}
Best Oratory Skills Award (Ryan)\\
Techno Savvy Award (Ryan)\\
\href{https://www.sololearn.com/certificates/CC-TJRFBFGZ}{Sololearn://Javascript}\\
\href{https://www.google.com}{Sololearn://C++}\\
\href{https://www.google.com}{HackerRank://SQL}\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{Stealth Startup}
\descript{DevOps Engineer | Full-time}
\location{April 2023 - Present | Canada, Remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Logs Review, Resources Install, Deployed and Managed Openstack.
\item Managing CI/CD, Docker, Kubernetes, ELK, BARE METAL Deployments.
\item MEAN and Monitoring Stacks, Active Monitoring, Linux Development. 
\item Developed Consul and Vault, other Hashicorps based secure tools.
\item Active Discovery, SSL Renew, Certbot,etc.
\end{tightemize}
\sectionsep

\runsubsection{Upwork INC.}
\descript{TOP RATED UPWORK FREELANCER}
\location{Oct 2022 - Present | Remote}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Stack Mastery: Proficient in DevOps, programming, CDN, and more.
\item Upwork Journey: Over the past 12 months on Upwork, I've earned 30,000+ USD with a stellar track record of 5-star reviews.
\item Industry Impact: Contributed to projects with major car manufacturers and Insurance companies, VPN Providers, Healthcare and Personal Projects.
\item Tech Stacks: Led projects using Python, Golang, Rust, and front-end technologies, Major Devops and Docker etc. projects.
\end{tightemize}
\sectionsep

\runsubsection{Wafercode Inc.}
\descript{Company Owner | Part-time}
\location{Jan 2023 – Present | Remote}
\begin{tightemize}
\item Owner and Team Lead at Wafercode, I lead a dedicated team of 5-10 professionals in delivering end-to-end solutions for business owners and startups.
\item Till Updation date, delivered 200+ projects, have consistently met client objectives and industry standards. 
\item Have excellent recurring and trusted clients whom we are thankful and promptly work with.
\end{tightemize}
\sectionsep

\runsubsection{Stealth Startup (Health-Tech)}
\descript{Golang Developer and DevOps Engineer | Full-time}
\location{Jan 2023 – Apr 2023 | United States, Remote}
\begin{tightemize}
\item Engineered a robust Golang-based system incorporating websockets for real-time communication in a health-focused application.    
\item Successfully deployed the full Application,API Gateway on Ubuntu based EC2 AWS and Digital Ocean as Failover.
\item Orchestrated containerized applications using Docker, optimizing scalability and resource utilization.
\end{tightemize}
\sectionsep

\runsubsection{Google Summer of Code 2022}
\descript{GSOC Intern@ Jitsi | Internship}
\location{May 2022 – Aug 2022 | United States, Remote}
\begin{tightemize}
\item Collaborated on the development of the Jitsi open-source project, a Python-based video conferencing platform (jitsi.org).
\item Implemented and maintained Bash scripts for seamless integration with cloud storage services, including Dropbox and Google Drive.
\item Enhanced the platform's functionality to enable the upload of meeting recordings to cloud storage upon user request.
\item Managed OAuth details from service providers, ensuring secure and reliable authentication mechanisms.
\end{tightemize}
\sectionsep
\end{minipage} 

% Add this line to start a new page
\newpage
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Hostel Managment System}
\descript{| Backend Developer FASTAPI Python}
\location{Feb 2023 –  Mar 2023 | }
Worked with Fellow CS Students to make a Hostel Managment System, solely made backend of App FASTAPI based CRUD System with Login and Logout. Used Python, MySQL, Cookies-Json Web Token.\textbf{\href{https://github.com/aayush-ag/dbms-hostel}{Github Link}}.  
\sectionsep

\runsubsection{Home and Cloud Lab Setup}
\descript{| System Architect and Administrator}
\location{Ongoing | Home and Cloud Environments}
\vspace{\topsep}
\begin{tightemize}
\item Designed and implemented a comprehensive home and cloud lab infrastructure for personal projects and experimentation.
\item Architectured deployment strategies for various applications, ensuring scalability, security, and high availability across on-premises and cloud environments.
\item Utilized technologies such as Docker, Kubernetes, FreeNAS, and ZFS pools to optimize resource utilization and data management.
\item Configured a media server for streaming and managing multimedia content.
\item Implemented a data warehouse for efficient data storage and retrieval in both local and cloud environments.
\item Hosted a variety of self-hosted applications for different purposes, including productivity tools, converters, and more.
\item Implemented Single Sign-On (SSO) using Keycloak with additional security provided by YubiKey for unified and secure authentication across services.
\item Configured and maintained around 100+ applications, ranging from small utilities to larger open-source projects.
\item Utilized Rclone to mount cloud storage services like Dropbox, Google Drive, and implemented rsync for backup solutions.
\item Implemented snapshot mechanisms for data protection and recovery.
\item Established a self-hosted VPN and SOCKS server hosted on a variety of servers for secure remote access.
\item Integrated a remote Windows VM using Proxmox for virtualization and management.
\item Implemented additional security measures, including YubiKey for authentication and encryption.
\item Configured a personal VPN for secure and private communication.
\item Documented the entire architecture and setup for future reference and knowledge sharing.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% \begin{tabular}{rll}
% 2014	     & top 52/2500  & KPCB Engineering Fellow\\
% 2014	     & 1\textsuperscript{st}/50  & Microsoft Coding Competition, Cornell\\
% 2013	     & National  & Jump Trading Challenge Finalist\\
% 2013     & 7\textsuperscript{th}/120 & CS 3410 Cache Race Bot Tournament  \\
% 2012     & 2\textsuperscript{nd}/150 & CS 3110 Biannual Intra-Class Bot Tournament \\
% 2011     & National & Indian National Mathematics Olympiad (INMO) Finalist \\
% \end{tabular}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Publications} 
% \renewcommand\refname{\vskip -1.5em} % Couldn't get this working from the .cls file
% \bibliographystyle{abbrv}
% \bibliography{publications}
% \nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
